A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 plots/cifar/aft_comparison.tex
update plots

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 527.37 & 0.72 & 527.37 & 1.83 & 0.97 \\
Cox & -- & 0.73 & -- & 0.85 & 0.32 \\
Log Logistic & 544.73 & 0.74 & 544.73 & 1.66 & 1.05 \\
Log Normal & 532.28 & 0.74 & 532.28 & 1.61 & 1.05 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1234.74 & -1234.74 & 0.79 & 0.80 & 0.00 & 0.00 \\
Cox & -- & -- & 0.80 & 0.80 & 0.00 & 0.00 \\
Log Logistic & -1335.65 & -1335.65 & 0.79 & 0.79 & 0.01 & 0.00 \\
Log Normal & -1387.92 & -1387.92 & 0.79 & 0.79 & 0.01 & 0.00 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-03-29 plots/cifar100/aft_comparison.tex
update plots

\begin{table*}
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 124.83 & 0.66 & 124.83 & 0.98 & 0.92 \\
Cox & -- & 0.67 & -- & 0.34 & 0.29 \\
Log Logistic & 80.29 & 0.68 & 80.29 & 0.98 & 0.95 \\
Log Normal & 76.14 & 0.67 & 76.14 & 0.98 & 0.95 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1113.16 & -1113.16 & 0.78 & 0.76 & 0.00 & 0.00 \\
Cox & -- & -- & 0.79 & 0.76 & 0.00 & 0.00 \\
Log Logistic & -1198.31 & -1198.31 & 0.78 & 0.77 & 0.01 & 0.00 \\
Log Normal & -1244.92 & -1244.92 & 0.79 & 0.77 & 0.01 & 0.00 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-03-29 plots/mnist/aft_comparison.tex
update plots

\begin{table*}
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t; \theta)$ \\
\midrule
Weibull & 133.22 & 0.80 & 133.22 & 2.10 & 0.81 \\
Cox & -- & 0.80 & -- & 0.63 & 0.28 \\
Log Logistic & 93.77 & 0.77 & 93.77 & 1.22 & 0.82 \\
Log Normal & 104.95 & 0.76 & 104.95 & 1.21 & 0.84 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1559.16 & -1559.16 & 0.90 & 0.90 & 0.00 & 0.00 \\
Cox & -- & -- & 0.90 & 0.89 & 0.00 & 0.00 \\
Log Logistic & -1672.54 & -1672.54 & 0.90 & 0.90 & 0.00 & 0.00 \\
Log Normal & -1711.45 & -1711.45 & 0.90 & 0.90 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table*}
